Dynamical Properties of Molecular-forming Gas Clumps in Galaxies at the Epoch of Reionization

### 2020-04-19 WRITEUP/ms_referee2.tex
remove boldface from 1st round

\begin{abstract}
We study the properties of molecular-forming gas clumps (MGCs) at the epoch of reionization using cosmological zoom-in simulations. We identify MGCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
%
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs. In \flower, the typical MGC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies. MGCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
%
In addition, we perform stability analysis to understand the origin and dynamical properties of MGCs. We find that MGCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in {\bf clouds} and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
%
Detailed studies of the star-forming gas dynamics at the epoch of reionization thus require a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array %mm2 (ALMA)
and the Next Generation Very Large Array.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) either directly from the cosmic web, or through mergers with other galaxies. This gas fuels \SF and feeds central supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
part of this material.
%
Existing studies indicate that early galaxies are more gas-rich with molecular fractions higher than those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of 
{\bf dense gas clumps in which molecules form quickly (hereafter molecular-forming gas clumps\footnote{{\bf Note that by clumps, 
we refer to kiloparsec-scale gas concentrations in galaxies, rather than molecular gas concentrations small than molecular clouds 
and containing cores.}}; 
MGCs)} that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}). Some theoretical works argue that the migration of such giant massive clumps through disks is largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

Earlier epochs still represent an essentially uncharted territory for ISM investigations. At present, it remains unclear how \SF proceeds in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6  which is responsible for producing the bulk of the UV photons that reionized the Universe.
{\bf High resolution hydrodynamics simulations have been carried out to investigate the global properties, structures,
and morphologies of galaxies out to the epoch of reionization (EoR) and their importance for providing
the ionizing photons \citep[see e.g.,][]{Ceverino17a, Katz17a, Ma18a, Trebitsch18a, Rosdahl18a}.
Compared to the zoom-in galaxies presented in these works,
the simulation used here focuses on a Lyman-break galaxy \citep{Pallottini17a} from the \ncode{serra} simulation suite
(see \citealt{Pallottini19a} for a comparison between these zoom-in simulations).
Most notably, we include a non-equilibrium thermo-chemical network to follow the formation of H$_2$, which is 
crucial to examining the properties of MGCs.
}

@@

The virial theorem for a distribution of unmagnetized gas can be written as \citep{McKee92a}
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot{\mathcal{I}} = 2(\mathcal{T} - \mathcal{T}_{\rm ext}) + \mathcal{W},
\end{equation}
where $\ddot{\mathcal{I}}$ is the second time derivative of the
Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of
the gas {\bf (including thermal, turbulent, and bulk motions)}, $\mathcal{T}_{\rm ext}$ is external pressure support, and
$\mathcal{W}$ is the gravitational energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm gas}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions. Defining $P_{\rm ext}$ as the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the kinetic energy, external pressure, and gravitational potential energy terms.

@@

In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass {\bf enclosed} within the MGC volume.

@@

The models include a non-equilibrium chemical network (\ncode{Krome}) following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$,
and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that the abundances are calculated using an on-the-fly non-equilibrium
formation of molecular hydrogen scheme described by \citet{Pallottini17a}.
{\bf In the simulation, the UV radiation field is assumed to be uniform spatially.
Self-shielding of H$_2$ from photo-dissociation is accounted for using the \citet{Richings14a} prescription,
while the formation rate on dust grain is computed following \citet{Jura75a}. Photo-dissociation via Lyman-Werner photons is included as
part of the \ncode{Krome} network. % (see \citealt{Bovino16a}).
We do not assume a clumping factor in the chemistry solver (i.e., $C_\rho$\eq1, cf. \citealt[][]{Lupi20a}).
In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.}
% (Section 2.1.1 of \citealt{Pallottini17b})}.

@@

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun 
(see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a})\footnote{The stellar mass-to-halo mass ratio for Althaea at $z$\eq6 is about 0.07. 
This is a factor of about 3 higher than the typical value inferred by abundance matching models, that typically gives $\sim0.02$. 
Note however that the ratio from abundance matching can vary; for instance, \citet{Behroozi13b} (main method) finds a ratio of 0.015\,--\,0.025 
is for a halo mass between $M_{\rm halo}$\ssim10$^{10.5}$--$10^{12}$\,\Msun, whereas in the same paper the authors find 
0.01--0.05 in the same mass range from direct abundance matching 
(see the Appendix therein). 
Additionally, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, i.e., within a factor 3 from \citet{Behroozi13b}.}. 
The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
}

@@

The mass of an MGC is calculated from the uniformly-gridded 3D density field, integrating over the MGC volume $V$. The effective size is defined assuming spherical geometry, i.e., $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MGCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MGCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating the global quantities of MGCs, we always perform a mass-weighting. Since we operate on data on a uni-grid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MGC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MGC.
We use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
%The bulk velocity dispersion is
%\begin{equation}
%\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
%\end{equation}
{\bf The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,,
\end{equation}
where \Eq{defineaverage} is applied to each velocity component.
}
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

We start by considering the distributions of MGC {\bf total gas mass $M_{\rm gas}$, radius $R$, and gas mass fraction}
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the distributions from the combination of the three considered evolution stages. We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut\footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MGC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MGC at this highest density threshold, so we consider MGCs identified with the second highest density threshold instead.} of $n_{\rm cut}$\eq18.96\,\cc (lower panels).
%
Overall, the mass of all MGCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun,
whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.

@@

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MGC}), which is identified as a single component at low $n_{\rm cut}$. This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is dominated by
{\bf the bulk motion term}\footnote{{\bf The bulk velocity dispersion term is likely associated with the rotational velocity, see \citet{Kohandel19a} for kinematical analysis of \flower.}}, as shown in \Fig{vv}, where we compare the velocity dispersions of MGCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MGC}).
%
Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MGCs in the accreting phase of \flower are dominated by turbulent motions, while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MGCs.
%
For these reasons, the most massive MGCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.

@@

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MGCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
%
The biggest MGC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MGC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability. On the other hand, the MGCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MGCs is comparable to the {\em total} virial parameter.}, with virial parameter {\bf within the range observed in the molecular structures
of the Milky Way but higher than its average value}, though the MGCs are more massive. {\bf The higher than typical MW value is linked to the higher turbulence of these systems.}

@@

At the highest density cut, only the densest gas structures are identified\footnote{\bf{In the simulation, the
densest molecular regions reaches gas density of $n_{\rm gas}$\ssim10$^3$\,\cc, which is comparable to the critical density
of low-$J$ CO lines (see e.g., \citealt{Vallini18a}); however, we emphasize that we do not resolve the internal structure of molecular clouds
at the resolution of the simulation.}}. The virial parameter of these MGCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more unstable against collapse (see middle right panel of \Fig{alpha16-28}).

>>>>

\begin{abstract}
We study the properties of molecular-forming gas clumps (MGCs) at the epoch of reionization using cosmological zoom-in simulations. We identify MGCs in a $z\simeq 6$ prototypical galaxy (``\flower'') using an H$_2$ density-based clump finder.
%
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs. In \flower, the typical MGC mass and size are $M_{\rm gas} \simeq 10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, which are comparable to those found in nearby spirals and starburst galaxies. MGCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms and pressure of $P/{\rm K}_B\simeq 10^{7.6}\,\rm K\,$\cc (i.e., $> 1000 \times$ with respect to the Milky Way), similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
%
In addition, we perform stability analysis to understand the origin and dynamical properties of MGCs. We find that MGCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in clouds and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
%
Detailed studies of the star-forming gas dynamics at the epoch of reionization thus require a spatial resolution of $\lesssim$40\,pc ($\simeq$\,0$\farcs$01), which is within reach with the Atacama Large (sub-)Millimeter Array %mm2 (ALMA)
and the Next Generation Very Large Array.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\section{Introduction}
The growth of galaxies and their subsequent evolution are governed by the baryon cycle---galaxies accrete gas from the intergalactic medium (IGM) either directly from the cosmic web, or through mergers with other galaxies. This gas fuels \SF and feeds central supermassive black holes. Subsequent feedback replenishes and enriches the circumgalactic medium by expelling some
part of this material.
%
Existing studies indicate that early galaxies are more gas-rich with molecular fractions higher than those of present-day galaxies \citep[e.g.,][]{vandevoort11b, Decarli16a, Decarli17a}. Massive gas inflows from the IGM trigger gravitational instabilities that lead to the formation of 
dense gas clumps in which molecules form quickly (hereafter molecular-forming gas clumps\footnote{Note that by clumps, 
we refer to kiloparsec-scale gas concentrations in galaxies, rather than molecular gas concentrations small than molecular clouds 
and containing cores.}; 
MGCs) that are typically more massive ($M_{\rm gas}\simeq 10^9$\,\Msun) and extended ($\simeq$ sub-kpc) than those observed in nearby galaxies (e.g., \citealt{Gabor13a, Hopkins14a, Inoue16a}). Some theoretical works argue that the migration of such giant massive clumps through disks is largely responsible for the buildup of the bulges of massive galaxies at redshift \z$\sim$\,0 \citep[e.g.,][]{Ceverino10a}.

@@

Earlier epochs still represent an essentially uncharted territory for ISM investigations. At present, it remains unclear how \SF proceeds in the (sub-)$L^*$ galaxy population at \z$\gtrsim$\,6  which is responsible for producing the bulk of the UV photons that reionized the Universe.
High resolution hydrodynamics simulations have been carried out to investigate the global properties, structures,
and morphologies of galaxies out to the epoch of reionization (EoR) and their importance for providing
the ionizing photons \citep[see e.g.,][]{Ceverino17a, Katz17a, Ma18a, Trebitsch18a, Rosdahl18a}.
Compared to the zoom-in galaxies presented in these works,
the simulation used here focuses on a Lyman-break galaxy \citep{Pallottini17a} from the \ncode{serra} simulation suite
(see \citealt{Pallottini19a} for a comparison between these zoom-in simulations).
Most notably, we include a non-equilibrium thermo-chemical network to follow the formation of H$_2$, which is 
crucial to examining the properties of MGCs.

@@

The virial theorem for a distribution of unmagnetized gas can be written as \citep{McKee92a}
\begin{equation}\label{eqn:virial_th_general}
\frac{1}{2}\ddot{\mathcal{I}} = 2(\mathcal{T} - \mathcal{T}_{\rm ext}) + \mathcal{W},
\end{equation}
where $\ddot{\mathcal{I}}$ is the second time derivative of the
Lagrangian moment of inertia, $\mathcal{T}$ is the internal energy of
the gas (including thermal, turbulent, and bulk motions), $\mathcal{T}_{\rm ext}$ is external pressure support, and
$\mathcal{W}$ is the gravitational energy.
%
Let us specialize to the case of a spherical self-gravitating molecular cloud of mass $M_{\rm gas}$, radius $R$, and root-mean-square velocity dispersion $\sigma$, accounting for both thermal and turbulent contributions. Defining $P_{\rm ext}$ as the external pressure, \Eq{virial_th_general} can be written as
\begin{equation}
\frac{1}{2}{\ddot{\mathcal{I}}} = 3 M \sigma^2 - 4\pi P_{\rm ext} R^3 - \Gamma\frac{GM^2}{R}\,,
\label{eqn:virial}
\end{equation}
where $\Gamma$ is a geometrical factor that is equal to 3/5 for a uniform sphere; in \Eq{virial} the terms on the right-hand side represent the kinetic energy, external pressure, and gravitational potential energy terms.

@@

In cases where a stellar component plays an important role in the dynamics, the virial parameter becomes
\begin{equation}
\alpha_{\rm vir, tot} \equiv \frac{5 R}{G (M_{\rm gas} + M_{\star})} \frac{M_{\rm gas} \sigma_{\rm gas}^2 + M_{\star} \sigma_\star^2}
					       {M_{\rm gas} + M_{\star} }\,,
\label{eqn:alpha_tot}
\end{equation}
where $M_\star$ is the stellar mass enclosed within the MGC volume.

@@

The models include a non-equilibrium chemical network (\ncode{Krome}) following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$,
and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that the abundances are calculated using an on-the-fly non-equilibrium
formation of molecular hydrogen scheme described by \citet{Pallottini17a}.
In the simulation, the UV radiation field is assumed to be uniform spatially.
Self-shielding of H$_2$ from photo-dissociation is accounted for using the \citet{Richings14a} prescription,
while the formation rate on dust grain is computed following \citet{Jura75a}. Photo-dissociation via Lyman-Werner photons is included as
part of the \ncode{Krome} network. % (see \citealt{Bovino16a}).
We do not assume a clumping factor in the chemistry solver (i.e., $C_\rho$\eq1, cf. \citealt[][]{Lupi20a}).
In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.
% (Section 2.1.1 of \citealt{Pallottini17b})}.

@@

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun 
(see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a})\footnote{{\bf The stellar mass-to-halo mass ratio for Althaea at $z$\eq6 is about 0.07. 
This is a factor of about 3 higher than the typical value inferred by abundance matching models, that typically gives $\sim0.02$. 
Note however that the ratio from abundance matching can vary; for instance, \citet{Behroozi13b} (main method) finds a ratio of 0.015\,--\,0.025 
is for a halo mass between $M_{\rm halo}$\ssim10$^{10.5}$--$10^{12}$\,\Msun, whereas in the same paper the authors find 
0.01--0.05 in the same mass range from direct abundance matching 
(see the Appendix therein). 
Additionally, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, i.e., within a factor 3 from \citet{Behroozi13b}.}.} 
The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.

@@

The mass of an MGC is calculated from the uniformly-gridded 3D density field, integrating over the MGC volume $V$. The effective size is defined assuming spherical geometry, i.e., $R \equiv (3 V /4 \pi)^{1/3}$.
%
The full velocity dispersion of MGCs is calculated from the bulk velocity field ($\sigma_{\rm bulk}$), thermal sound speed ($c_s$), and the non-thermal velocity dispersion ($\sigma_{\rm NT}$)
\begin{equation}
\sigma_{\rm gas}^2 = \sigma_{\rm bulk}^2 + c_s^2 + \sigma_{\rm NT}^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MGCs, the linewidth contribution of dense gas exceeds that from the diffuse gas. Therefore, when calculating the global quantities of MGCs, we always perform a mass-weighting. Since we operate on data on a uni-grid, this is equivalent to density averaged quantities. In general, for the quantity $x$ in a MGC we write
\begin{equation}\label{eqn:defineaverage}
\langle x \rangle \equiv \frac{\sum_{i} \rho_i x_i }{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells indexed by $i$ composing the MGC.
We use the definition \Eq{defineaverage} to write each term of the right-hand side of Equation~\ref{eqn:veldisp} as follows.
%
%The bulk velocity dispersion is
%\begin{equation}
%\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,.
%\end{equation}
The bulk velocity dispersion is
\begin{equation}
\sigma_{\rm bulk}^2 = \frac{1}{{3}} \langle \left|\mathbf{v} - \langle \mathbf{v} \rangle  \right|^2\rangle \,,
\end{equation}
where \Eq{defineaverage} is applied to each velocity component.
%
The thermal sound speed is calculated from the thermal pressure ($P_{\rm TH}$) through
\begin{equation}
c_s^2 = \left\langle \frac{{\rm k_B} ~P_{\rm TH}}{{\rm m_p}\, n} \right\rangle\,,
\end{equation}
where the pressure is in units of K\,\cc, $\rm k_B$ is the Boltzmann constant, $m_p$ is the mass of a proton. Similarly, contribution from non-thermal energy is calculated from non-thermal pressure ($P_{\rm NT}$) as follows
\begin{equation}
\sigma_{\rm NT}^2 = \left\langle \frac{{\rm k_B} ~P_{\rm NT}}{{\rm m_p}\, n}\right\rangle\,.
\end{equation}
%
Finally, the Mach number is related to the pressure terms as follows
\begin{equation}
\mathcal{M} = \left\langle \sqrt{ 1 + \frac{P_{\rm NT}}{P_{\rm TH}}} \right\rangle.
\label{eqn:MPress}
\end{equation}

@@

We start by considering the distributions of MGC total gas mass $M_{\rm gas}$, radius $R$, and gas mass fraction
\begin{equation}
f_{\rm gas} = \frac{M_{\rm gas}} {\left(M_{\rm gas} + M_\star\right)}.
\end{equation}
%
We show in \Fig{dist} the distributions from the combination of the three considered evolution stages. We show results for a low density cut of $n_{\rm cut}$\eq0.32\,\cc (top panels) and a high cut\footnote{The highest density threshold we used of $n_{\rm cut}$\eq31.62\,\cc corresponds to a minimum MGC mass of the order of 10$^{5.5}$\,\Msun for the densest structure. However, not all evolutionary stages considered have at least one MGC at this highest density threshold, so we consider MGCs identified with the second highest density threshold instead.} of $n_{\rm cut}$\eq18.96\,\cc (lower panels).
%
Overall, the mass of all MGCs identified ranges from $M_{\rm gas}\simeq$10$^{5.5-8.5}$\,\Msun,
whereas the gas fraction ranges from $f_{\rm gas} \simeq$\,0.1\,--\,1.

@@

The most massive structures ($M_{\rm gas}>$10$^7$\,\Msun) correspond to the molecular disk of the galaxy (see e.g., \Fig{MGC}), which is identified as a single component at low $n_{\rm cut}$. This main disk component occupies the top left corner of \Fig{stellarRatio16}, with a low gas mass fraction of $f_{\rm gas}< 5\%$. The velocity dispersion of such a structure is dominated by
the bulk motion term\footnote{The bulk velocity dispersion term is likely associated with the rotational velocity, see \citet{Kohandel19a} for kinematical analysis of \flower.}, as shown in \Fig{vv}, where we compare the velocity dispersions of MGCs resulting from bulk ($\sigma_{\rm bulk}$) versus non-thermal turbulent motions ($\sigma_{\rm NT}$) in the accreting and quiescent phases of \flower. The accreting phase of \flower displays a disturbed morphology, whereas the quiescent phase displays a disk-like morphology (\Fig{MGC}).
%
Excluding the structure corresponding to the molecular disk, the velocity dispersions of most MGCs in the accreting phase of \flower are dominated by turbulent motions, while  in the quiescent disk-like phase, $\sigma_{\rm bulk}$ is at least comparable to $\sigma_{\rm NT}$ for almost half the MGCs.
%
For these reasons, the most massive MGCs are excluded in the discussion of the dynamics (\Sec{diss}), as they are dominated by large-scale shear; however, we include them in the scaling relation plots (\Fig{larsons_single} and \Fig{alpha16-28}), as would be done for an observational study.

@@

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MGCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
%
The biggest MGC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MGC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability. On the other hand, the MGCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MGCs is comparable to the {\em total} virial parameter.}, with virial parameter  within the range observed in the molecular structures
of the Milky Way but higher than its average value, though the MGCs are more massive. 
The higher than typical MW value is linked to the higher turbulence of these systems.

@@

At the highest density cut, only the densest gas structures are identified\footnote{In the simulation, the
densest molecular regions reaches gas density of $n_{\rm gas}$\ssim10$^3$\,\cc, which is comparable to the critical density
of low-$J$ CO lines (see e.g., \citealt{Vallini18a}); however, we emphasize that we do not resolve the internal structure of molecular clouds
at the resolution of the simulation.}. The virial parameter of these MGCs are, on average, lower than those identified at low $n_{\rm cut}$, and are thus, more unstable against collapse (see middle right panel of \Fig{alpha16-28}).
